---
title: "Rental Listing Inquiries"
output: html_document
---

# data import
```{r data import}
## data import
packages <- c("jsonlite", "dplyr", "purrr", "tidytext", "ggplot2", "ggthemes",
              "RecordLinkage","sampling", "xgboost", "RCurl", "ROCR")
purrr::walk(packages, library, character.only = TRUE, warn.conflicts = FALSE)
# "rattle",
read.fromJson <- function(filepath){
  data <- fromJSON(filepath)
  var <- setdiff(names(data), c("photos","features"))
  data <- map_at(data, var, unlist) %>%
    tibble::as_tibble(.) %>%
    mutate(feature_count = lengths(features)) %>%
    mutate(photo_count = lengths(photos)) %>%
    select(-features, -photos) %>%
    data.frame
}

rental_data <- read.fromJson("train.json")

## data exploration
glimpse(rental_data)
```

From information of rental, we use use the counter of photos and features, to replace them.

# data explore
```{r data explore}
theme_set(theme_economist())
plot.theme <- theme(
  legend.position = "bottom",
  axis.text.x=element_text(size=12),
  axis.text.y=element_text(size=12),
  axis.title.x=element_text(size=14),
  axis.title.y=element_text(size=14),
  axis.title = element_text(size=16, vjust=3),
  plot.title = element_text(hjust = 0.5)
)
rental_data %>%
  group_by(interest_level) %>%
  count() %>%
  arrange(desc(n)) %>%
  ggplot(aes(x=interest_level, y=n, fill=interest_level)) +
  geom_bar(stat="identity") +
  labs(x = "interest level", y = "Freq", title = "The distribution of interse level") +
  geom_text(aes(label = n, vjust=-0.2)) +
  plot.theme


rental_data %>%
  group_by(interest_level, bathrooms) %>%
  count() %>%
  arrange(desc(bathrooms)) %>%
  ggplot(aes(x=as.character(bathrooms), y=n, fill=bathrooms)) +
  geom_bar(stat="identity") +
  facet_wrap(~interest_level) +
  coord_flip() +
  labs(x = "bath room count", y = "Freq", title = "The distribution of bath rooms number by interest level") +
  geom_text(aes(label = n, hjust=-0.2)) +
  plot.theme

rental_data %>%
  group_by(interest_level, feature_count) %>%
  count() %>%
  arrange(desc(feature_count)) %>%
  ggplot(aes(x=as.factor(feature_count), y=n, fill=feature_count)) +
  geom_bar(stat="identity") +
  facet_wrap(~interest_level) +
  coord_flip() +
  labs(x = "feature count", y = "Freq", title = "fatures count interset level") +
  geom_text(aes(label = n, hjust=0.5)) +
  theme(legend.position = "bottom")  +
  plot.theme


rental_data %>%
  group_by(interest_level, photo_count) %>%
  count() %>%
  arrange(desc(photo_count)) %>%
  ggplot(aes(x=as.factor(photo_count), y=n, fill=photo_count)) +
  geom_bar(stat="identity") +
  facet_wrap(~interest_level) +
  coord_flip() +
  labs(x = "photo count", y = "Freq", title = "photos count by interset level") +
  geom_text(aes(label = n, hjust=-0.2)) +
  plot.theme
```


# outlier detection
```{r outlier detection}
detect_outlier <- function(column) {
  iqr = quantile(column, .75) - quantile(column, .25)
  low = quantile(column, .25) - 1.5 * iqr
  high = quantile(column, .75) + 1.5 * iqr
  outlier_index = ifelse(column < low | column > high, TRUE, FALSE)
  results <- list("index" = outlier_index, "values"  = column[outlier_index], 'low' = low, 'high' = high, 'iqr' = iqr)
  return(results)
}

rental_data %>%
  ggplot(aes(x=interest_level, y=price)) +
  geom_violin((aes(fill = interest_level))) +
  geom_boxplot(width=.1, fill="black", outlier.color="red") +
    stat_summary(fun.y=median, geom="point",
                 fill="blue", shape=21, size=2.5) +
  ylim(0, quantile(rental_data$price, .99)) +
  plot.theme


rental_data %>%
  ggplot(aes(x=interest_level, y=longitude)) +
  geom_violin((aes(fill = interest_level))) +
  geom_boxplot(width=.1, fill="black", outlier.color="red") +
  stat_summary(fun.y=median, geom="point",
               fill="blue", shape=21, size=2.5) +
  ylim(0, quantile(rental_data$longitude, .99)) +
  plot.theme

rental_data %>%
  ggplot(aes(x=interest_level, y=latitude)) +
  geom_violin((aes(fill = interest_level))) +
  geom_boxplot(width=.1, fill="black", outlier.color="red") +
  stat_summary(fun.y=median, geom="point",
               fill="blue", shape=21, size=2.5) +
  ylim(0, quantile(rental_data$latitude, .99)) +
  plot.theme


# From the numer plot, we should deal with the outlier observations.

rental_data <- rental_data %>%
  filter(!detect_outlier(price)$index) %>%
  filter(!detect_outlier(latitude)$index) %>%
  filter(!detect_outlier(longitude)$index)


rental_data %>%
  ggplot(aes(x=price, y=..density..)) +
  geom_histogram(fill="cornsilk", colour="red", size=.2,
                 binwidth = diff(range(rental_data$price))/20) +
  geom_density() +
  facet_grid(.~interest_level) +
  labs(title = "The distribution of price by interset level") +
  plot.theme

rental_data %>%
  ggplot(aes(x=latitude, y=..density..)) +
  geom_histogram(fill="cornsilk", colour="red", size=.2,
                 binwidth = diff(range(rental_data$latitude))/20) +
  geom_density() +
  facet_grid(.~interest_level) +
  labs(title = "The distribution of latitude by interset level") +
  plot.theme

rental_data %>%
  ggplot(aes(x=longitude, y=..density..)) +
  geom_histogram(fill="cornsilk", colour="red", size=.2,
                 binwidth = diff(range(rental_data$longitude))/20) +
  geom_density() +
  facet_grid(.~interest_level) +
  labs(title = "The distribution of latitude by interset level") +
  plot.theme
```


From the boxplot and violin above, there are some outlier points in observations, therefore, we use the the Interquartile Range Rule to exclude them.

# var transform
```{r var transform}
# Variable Transform

##1. Creating Features from Street Address and Display Address
rental_data <- rental_data %>%
  mutate(distance = levenshteinSim(tolower(street_address),tolower(display_address))) %>%
  select(bathrooms, bedrooms,latitude, longitude, price, interest_level, feature_count, photo_count, distance) %>%
  mutate(distance = ifelse(is.na(distance), 0, distance))


na.omit(rental_data) %>%
  ggplot(aes(x=distance, y=..density..)) +
  geom_histogram(fill="cornsilk", colour="red", size=.2) +
  geom_density() +
  facet_grid(.~interest_level) +
  labs(title = "The distribution of distance by interset level") +
  plot.theme
```

- The Levenshtein distance is a string metric for measuring the difference between two sequences.  therefore, we create a new feature the similarity between the street address and the display address using the Levenshtein distance.

# data partition

```{r data partition}
sample.flag <- strata(rental_data, stratanames = "interest_level",
                      size = 3*rep(min(table(rental_data$interest_level)),3),
                      method = "srswr")


## data partition
rental_data <- na.omit(rental_data)
train.data <- na.omit(rental_data[sample.flag$ID_unit,]) %>%
  mutate(interest_level = factor(interest_level)) %>%
  sample_frac(1)
test.data <- na.omit(rental_data[-sample.flag$ID_unit,]) %>%
  mutate(interest_level = factor(interest_level)) %>%
  sample_frac(1)


train_matrix <- Matrix::sparse.model.matrix(interest_level ~ .-1, data = train.data)

test_matrix <- Matrix::sparse.model.matrix(interest_level ~ .-1, data = test.data)

dtrain <- xgb.DMatrix(train_matrix,
                      label = as.integer(as.factor(train.data$interest_level))-1)
dtest <- xgb.DMatrix(test_matrix, label = as.integer(as.factor(test.data$interest_level))-1)
label.train <- train.data$interest_level
label.test <- test.data$interest_level
```

The distribution of interest_level is some incline, high score is only 7.4% percent. Therefore, we use resample to get the train data with the stratified sampling replacement, change the distribution of high in interest_level.
	
# xgboost
## xgboost treee model
```{r xgboost treee model}

param <- list(objective = "multi:softprob",
              booster="gbtree", eval_metric = "merror",
              max.depth = 100,eta = 0.1, nthread =8,
              alpha=0.01)

watchlist <- list(eval = dtest, train = dtrain)

system.time(
  fit.xgboost.tree <- xgb.train(
    nrounds = 100,
    verbose = 1,
    params = param,
    num_class = 3,
    dtrain,
    watchlist)
)

```


xgboost tree model

## model prediction
```{r model prediction}
predict_data <- read.fromJson("test.json") %>%
    mutate(distance = levenshteinSim(tolower(street_address),tolower(display_address))) %>%
  mutate(distance = ifelse(is.na(distance), 0, distance)) %>%
  select(bathrooms, bedrooms,latitude, longitude, price, feature_count, photo_count, distance) %>%
  mutate(interest_level = " ")
predict.matrix <- Matrix::sparse.model.matrix(interest_level ~ .-1, data = predict_data)

tree.predict <- predict(fit.xgboost.tree, predict.matrix)

Y.tag = 1:length(tree.predict) %%3 + 1
high <- tree.predict[Y.tag==2]
low <- tree.predict[Y.tag==3]
medium <- tree.predict[Y.tag==1]
listing_id <- read.fromJson("test.json")$listing_id
tree.predict.df <- data.frame(listing_id, high, low, medium)
# tree.predict.df$interest_level <- factor(apply(tree.predict.df, 1,                                      function(x) which.max(x) - 1))
# 
# levels(tree.predict.df$interest_level) <- c("high", "low", "medium")
# tree.predict.df$interest_level <- as.character(tree.predict.df$interest_level)

write.csv(tree.predict.df, "predict_df.csv",row.names = FALSE)

tree.predict.df %>%
  sample_n(20) %>%
  knitr::kable(caption = "The 20 sample of predict of xgboost linear model")
```
